
\documentclass[margin, centered]{resume}

\begin{document}
\name{\Huge Jilong Liao}
\address{\\
\textbf{Email}: jilong.liao@outlook.com \hspace{50mm}\hfill \textbf{Address}: 16340 NE 83rd St.\\
\textbf{Phone}: 865-360-6082 \hfill Apt D-221\\
\textbf{Home Page}: http://jilongliao.com \hfill Redmond WA, 98052
}
\begin{resume}

    \section{\mysidestyle Education}

    \textbf{The University of Tennessee}, Knoxville, TN \hfill Jan 2011 -- Dec 2013\\
    \emph{Master's in Computer Science}
    \begin{list2}
        \item Major GPA: 3.8/4.0
        \item Thesis: \emph{A Privacy-Aware Distributed Storage and Replication Middleware for Heterogeneous Computing Platform}
    \end{list2}
    \textbf{University of Electronic Science and Technology of China}(UESTC) \hfill Sept 2006 -- Jul 2010\\
	\emph{Bachelor's in Communication Engineering with Honors}
	\begin{list2}
		\item Major GPA: 3.9/4.0
	\end{list2}\vspace{-1mm}

    \section{\mysidestyle Professional\\Experience}

    \textbf{Microsoft}, Redmond, WA
    \emph{Software Development Engineer} \hfill Jan 2014 -- Present \\
    $\bullet$ Work in Windows Fundamental/Data Apps team. 

    \textbf{The University of Tennessee}, Knoxville, TN \\
    \emph{Research Assistant} \hfill Jan 2011 -- Dec 2013\\
    $\bullet$ Research into projects includes mobile computing, machine learning and distributed system

    \textbf{Microsoft}, Redmond, WA \\
    \emph{Software Development Engineer Intern} \hfill May 2013 -- Aug 2013 \\
    $\bullet$ Project: Component Power Characterization Suite for SoC System\\
    $\bullet$ Designed a generic and scalable framework which built in CPU, memory and GPU component\\
    $\bullet$ Extended the framework to muti-variant and performance analysis metrics support 

    \textbf{The University of Tennessee}, Knoxville, TN \\
    \emph{Teaching Assistant} \hfill Jan 2011 -- Dec 2011\\
    $\bullet$ Taught undergraduate students C++ programming and graded students' homework
	
    \textbf{Ericsson (China) Communications Co.}, Chengdu, China \\%
	\emph{Integration/Verification Engineer Intern} \hfill Dec 2009 -- Mar 2010\\
    $\bullet$ Integrated TD-SCDMA base-station system and fixed one software bug

    \section{\mysidestyle Professional \\Skill} 
	
	\textbf{Familiar with}: Software Engineering, Machine Learning, Big Data Tools, Distributed System, Android, MySQL\\
    \textbf{Strong Language}: C/C++(7 yrs), Java(4 yrs), Python(4 yrs)

    \section{\mysidestyle Publications}
    \begin{enumerate}
    \item Y. Yao, S. Xiong, J. Liao, Q. Cao, and M. Berry, ``Identifying Frequent Flows in Large Traffic Sets through Probabilistic Bloom Filters'', submitted to the 34th International Conference on Distributed Computing Systems (ICDCS’14). 
    \item J. Liao, Z. Wang, L. Wan, Q. Cao, and H. Qi, ``Smart Diary: A Smartphone-based Framework for Inference and Prediction of Users’ Behaviors'', submitted to IEEE Sensors Journal. 
    \item X. Ma, J. Liao, S. Djouadi, and Q. Cao, ``LIPS: Link Prediction as a Service for Data Aggregation Applications'', \emph{Journal of Ad Hoc Networks (Elsevier)}, 2014. 
    \item Z. Wang, J. Liao, Q. Cao, H. Qi and Z. Wang, ``Achieving k-barrier Coverage in Hybrid Directional Sensor Networks'', \emph{IEEE Transactions on Mobile Computing (TMC)}, 2013. 
    \item J. Liao, K. Lu and Q. Cao, ``Uno: A Privacy-Aware Distributed Storage and Replication Middleware for Heterogeneous Computing Platforms'', \emph{IEEE MASS}, 2013.  
    \item Z. Wang, J. Liao, Q. Cao, H. Qi and Z. Wang, ``Barrier Coverage in Hybrid Directional Sensor Networks'', \emph{IEEE MASS}, 2013. 
    \item J. Liao, Z. Wang, Q. Cao and H. Qi, ``Smart Diary: the Narrative of Your Daily Life'', \emph{NSF Southeastern Workshop on Cognitive Sensing, Computing and Networking and Their Applications in Human-Cyber-Physical Systems}, Tuscaloosa, Alabama. August 15, 2012.  
    \item J. Liao and Q. Cao, ``Demo Abstract: Uno - A Sharing Infrastructure for Smartphone Sensors and Files'', \emph{ACM SenSys}, 2011.
    \end{enumerate}

    \section{\mysidestyle Citations}
    Details can be found on Google Scholar author page: \\
    http://scholar.google.com/citations?user=OrW2SEgAAAAJ\&hl=en
    
    \section{\mysidestyle Academic Services}
    \begin{enumerate}
    \item Reviewer, IEEE International Conference on Computer Communications (INFOCOM) \hfill 2014
    \item Reviewer, International Conference on Wireless Sensor Networks for Developing Countries \hfill 2013
    \item Reviewer, IEEE Journal of Communications and Networks (JCN) \hfill 2013
    \item Reviewer, IEEE International Conference on Mobile Ad-hoc and Sensor Systems (MASS) \hfill 2012
    \item Reviewer, IEEE International Conference on Mobile Ad-hoc and Sensor Networks (MSN) \hfill 2011
    \end{enumerate}

    \section{\mysidestyle Honours and\\Awards} 
    \begin{enumerate}
    \item \textsl{Chancellor's Citations for Extraordinary Professional Promise}, awarded by the Chancellor of University of Tennessee, Knoxville for extraordinary professional performance. \hfill 2013 
    \item \textsl{EECS Department Excellent Fellowship}, awarded by the EECS department of University of Tennessee, Knoxville for excellent academic performance. \hfill 2012, 2011
    \item \textsl{ACM SenSys Student Travel Grant}, awarded by the ACM SenSys Conference for students who published papers in the conference. \hfill 2011
    \item \textsl{Second Prize}, the $8^{th}$ UESTC Programming Contest \hfill 2010
    \item \textsl{Outstanding Graduation Honor} \hfill 2010
    \item \textsl{National Fellowship} \hfill 2009, 2008
    \item \textsl{Bronze Medal}, the $33^{rd}$ \textbf{ACM-ICPC} Asia Regional Contest (Beijing) \hfill 2008
    \end{enumerate}

\end{resume}
\end{document}
